# Missing values

## movie data from IMDB
```{r}
library(tidyverse)
library(redav)
library(ggplot2)
```

*Top five rows for a brief view on IMDB dataset*
```{r}
# imdb
movie_IMDB = read_csv("movie_IMDB.csv")
head(movie_IMDB)
```
*Check the sum of missing value*
```{r}
# check the sum of missing value
sum(is.na(movie_IMDB))
```
*Provides summary statistics on the columns of the data frame, this will also give details on missing values for each column*
```{r}
# provides summary statistics on the columns of the data frame, this will also give details on missing values for each column
summary(movie_IMDB)
```

*visualize the number of missing intuitively and clearly using plot_missing from redav*
```{r}
# visualize the number of missing using plot_missing from redav
# rows and columns sorted by number missing
plot_missing(movie_IMDB, percent = FALSE)

```

## Movie data from Douban
*Top five rows for a brief view on IMDB dataset*
```{r}
# douban movie
movie_high= read_csv("movie_high.csv")
movie_median= read_csv("movie_median.csv")
movie_low= read_csv("movie_low.csv")
movie_douban = rbind(movie_high,movie_median)
movie_douban = rbind(movie_douban,movie_low)
head(movie_douban)
```
*Check the sum of missing value*
```{r}
# check the sum of missing value
sum(is.na(movie_douban))
```
*Provides summary statistics on the columns of the data frame, this will also give details on missing values for each column*
```{r}
# provides summary statistics on the columns of the data frame, this will also give details on missing values for each column
summary(movie_douban)
```

*visualize the number of missing intuitively and clearly using plot_missing from redav*
```{r}
# visualise the number of missings using plot_missing from redav
# rows and columns sorted by number missing
plot_missing(movie_douban, percent = FALSE)
```

## Explanation of Missing Value Pattern
From the above results, we find there exists no missing pattern in both datasets. This is mostly because we captured the data we need through web crapping from the websites pages by pages dynamically, from which the missing values were all removed inside the loops since they have no text values.