# Interactive component

```{r}
library(tidyverse)
library(ggplot2)
library(plotly)
```

```{r}
# imdb
movie_IMDB = read_csv("movie_IMDB.csv")
movie_high= read_csv("movie_high.csv")
movie_median= read_csv("movie_median.csv")
movie_low= read_csv("movie_low.csv")
movie_douban = rbind(movie_high,movie_median)
movie_douban = rbind(movie_douban,movie_low)
#head(movie_douban)
#head(movie_IMDB)
```

## Genre Changes over Time
### IMDB
```{r}
# split the genre column into three new columns: genre_1, genre_2, genre_3, note, some movies do not have value in genre_2 or genre_3
movie_IMDB_split_genre <- movie_IMDB %>%
  separate(genre, c("genre_1", "genre_2", "genre_3"))

#head(movie_IMDB_split_genre)

# we also need a tibble that with one column genre but store one genre in each row
movie_IMDB_split_mutirows <- movie_IMDB_split_genre %>%
  pivot_longer(genre_1:genre_3, names_to = "genre_order", values_to = "genre_i") %>%
  drop_na() %>%
  filter(genre_i != "Fi")

#head(movie_IMDB_split_mutirows)

# find the top 10 favorite genres
movie_genre_top10 <- movie_IMDB_split_mutirows %>%
  group_by(genre_i) %>%
  summarise(total_counts = n()) %>%
  arrange(-total_counts) %>% 
  top_n(10)

#movie_genre_top10


# view the trend of top 10 genres by year
movie_genre_top10_by_year <- left_join(movie_IMDB_split_mutirows,movie_genre_top10, by = "genre_i") %>%
  drop_na() %>%
  group_by(year, genre_i) %>%
  summarize(quantity = n())

#movie_genre_top10_by_year
# find the top

fig <- movie_genre_top10_by_year %>%
  ungroup() %>%
  plot_ly(x = ~year, y = ~quantity, color = ~genre_i, type = 'scatter',  mode = 'lines+markers', line = list(width = 1)) %>%
  layout(title = "Trends of Top 10 Genres from 1920 to 2022(IMDB)",
         yaxis = list(title = "Quantities of Genres per year"),
         xaxis = list(title = "Year"))


fig

```

**Interactive line plot instructions** \
*a. Move your mouse to each points will show out the genre, the Year,and the total count of this genre in this year* \
*b. Click the legend you wand to disappear or appear the data for the genres*


**Infer** \
From this interactive lines plot on Trends of Top 10 Genres from 1920 to 2022(IMDB), we also derived that that: \
1. Drama seems to be the most popular genre. \
2. Compared with other film genres, the number of Drama in the top 700 list is several times or even a dozen times higher than other genres almost every year. \
3. In the top 700 list, each genre occupies in the range of [0,18] in each year. \
4. The number of films in all genres changed little before 1960, but grew dramatically from the 1990s onward, with significant growth in the number of films in the top five categories of Drama, Comedy, Thriller, Adventure, and Romance. After peaking around 2010, the number of movies has declined overall in recent years.


### Douban
```{r}
# split the genre column into three new columns: genre_1, genre_2, genre_3, note, some movies do not have value in genre_2 or genre_3
movie_DB_split_genre <- movie_douban %>%
  separate(Type, c("genre_1", "genre_2", "genre_3"))

#head(movie_DB_split_genre)

# we also need a tibble that with one column genre but store one genre in each row
movie_DB_split_mutirows <- movie_DB_split_genre %>%
  pivot_longer(genre_1:genre_3, names_to = "genre_order", values_to = "genre_i") %>%
  drop_na()

#head(movie_DB_split_mutirows)

# find the top 10 favorite genres
movie_genre_top10 <- movie_DB_split_mutirows %>%
  group_by(genre_i) %>%
  summarise(total_counts = n()) %>%
  arrange(-total_counts) %>% 
  top_n(10)

#movie_genre_top10


# view the trend of top 10 genres by year
movie_genre_top10_by_year <- left_join(movie_DB_split_mutirows,movie_genre_top10, by = "genre_i") %>%
  drop_na() %>%
  group_by(Year, genre_i) %>%
  summarize(quantity = n())

#movie_genre_top10_by_year
# find the top

fig <- movie_genre_top10_by_year %>%
  ungroup() %>%
  plot_ly(x = ~Year, y = ~quantity, color = ~genre_i, type = 'scatter',  mode = 'lines+markers', line = list(width = 1)) %>%
  layout(title = "Trends of Top 10 Genres from 1920 to 2022 (Douban)",
         yaxis = list(title = "Quantities of Genres per year"),
         xaxis = list(title = "Year"))


fig

```

**Interactive line plot instructions** \
*a. Move your mouse to each points will show out the genre, the Year,and the total count of this genre in this year* \
*b. Click the legend you wand to disappear or appear the data for the genres*


**Infer** \
From this interactive lines plot on Trends of Top 10 Genres from 1920 to 2022 (Douban), **we could select different genres to make them hidden or appear**, we also derived that that: \
1. For both website, Drama is the mainly genre in the movie market in every year. Thie may because some movies would have more than one genre, and Drama would be the most recapitulative type. \
2. There are some difference genres of the top 10 genre, however, most of them are the same. \
3. We can see that these genres increase withn fluctuation, and there is a rapid drop during the 2019-2020, because of the epidemic, the movie market is almost at standstill. \


